---
title: "Regression"
output:
  pdf_document: default
  html_document: default
date: '2022-06-11'
---



### Q1

## Loading csv file

```{r echo=TRUE,message=FALSE}
options(warn = -1)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
df <- read_csv("C://Users//Amit//Downloads//Data11.csv")  # here put file location 

df2 <- df %>%  dplyr::select(IMPACT, SUBSTANCE, MEANINGFUL_COMPARISON, ORIGINALITY,RECOMMENDATION, 
                             SOUNDNESS_CORRECTNESS, CLARITY, REVIEWER_CONFIDENCE, APPROPRIATENESS)

df1 <- df %>% select(IMPACT, SUBSTANCE, MEANINGFUL_COMPARISON, ORIGINALITY,RECOMMENDATION, 
                     SOUNDNESS_CORRECTNESS, CLARITY, REVIEWER_CONFIDENCE, APPROPRIATENESS)
```

## Classify reviewer confidence to 0 or 1

```{r echo=TRUE,message=FALSE}

df1$REVIEWER_CONFIDENCE[df1$REVIEWER_CONFIDENCE<4] <- 0
df1$REVIEWER_CONFIDENCE[df1$REVIEWER_CONFIDENCE>=4] <- 1
```

## Split the data to train and test


```{r echo=TRUE,message=FALSE}

sample <- sample(c(TRUE, FALSE), nrow(df1), replace=TRUE, prob=c(0.7,0.3))
train  <- df1[sample, ]
test   <- df1[!sample, ]
```


## Logistic Regression


```{r echo=TRUE,message=FALSE}
model <- glm(REVIEWER_CONFIDENCE ~ IMPACT + SUBSTANCE + APPROPRIATENESS+  MEANINGFUL_COMPARISON +
               RECOMMENDATION+ 
               ORIGINALITY +  SOUNDNESS_CORRECTNESS + CLARITY , data = train, family = "binomial")
fitted.results <- predict(model,test,type='response')
fitted.results1 <- ifelse(fitted.results > 0.75,1,0)
```


## ROC curve and PRC curve


```{r echo=TRUE,message=FALSE}

library(precrec)
m <- evalmod(scores=fitted.results1,labels=test$REVIEWER_CONFIDENCE)
autoplot(m)

aucs <- auc(m)
knitr::kable(aucs)

```


## confusion matrix

```{r echo=TRUE,message=FALSE}

library(caret)
library(InformationValue)
library(ISLR)
confusionMatrix(fitted.results1,test$REVIEWER_CONFIDENCE)


```



##  Estimating the success of the Logistic Regression with different tests
```{r echo=TRUE,message=FALSE}


 
error_metric=function(CM)
{
   
  TN =CM[1,1]
  TP =CM[2,2]
  FP =CM[1,2]
  FN =CM[2,1]
  precision =(TP)/(TP+FP)
  accuracy_model  =(TP+TN)/(TP+TN+FP+FN)
  recall = (TP)/(TP+FN)
  f1 = (2*(precision*recall))/(precision+recall)
  print(paste("Recall value of the model: ",round(recall,2)))
  print(paste("Precision value of the model: ",round(precision,2)))
  print(paste("Accuracy of the model: ",round(accuracy_model,2)))
  print(paste("f1 of the model: ",round(f1,2)))

   
}
CM=table(test$REVIEWER_CONFIDENCE,fitted.results1)
error_metric(CM)
```


##  Feature selection for multiple linear regression


## perform k-fold cross-validation to find optimal lambda value

```{r echo=TRUE,message=FALSE}

library(glmnet)
y<- df2$REVIEWER_CONFIDENCE
x <- data.matrix(df2[,c('IMPACT' ,'SUBSTANCE' , 'MEANINGFUL_COMPARISON','RECOMMENDATION', 
                        'ORIGINALITY','APPROPRIATENESS',  'SOUNDNESS_CORRECTNESS', 'CLARITY')])


cv_model <- cv.glmnet(x, y, alpha = 1)
```


## Find optimal lambda value that minimizes test MSE

```{r echo=TRUE,message=FALSE}
best_lambda <- cv_model$lambda.min
best_lambda
```

## Plotting lambda and the coefficients of the independent varibales

```{r echo=TRUE,message=FALSE}
plot(cv_model)
best_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
print(coef(best_model))
```


## Multiple linear regression based on the feature selection



```{r echo=TRUE,message=FALSE}

ggplot(df2, aes(x = CLARITY+IMPACT+SUBSTANCE+ORIGINALITY+
                  APPROPRIATENESS+RECOMMENDATION,  y = REVIEWER_CONFIDENCE,color=IMPACT)) + 
  geom_smooth(method="lm",col = "light blue3")+theme_light()+
  theme(axis.title.x = element_text(size = 10)) +
  labs(x= "CLARITY+IMPACT+SUBSTANCE+ ORIGINALITY+APPROPRIATENESS+RECOMMENDATION",
       title ="Linear regression")                                           
 

model1 <- lm(REVIEWER_CONFIDENCE ~ IMPACT + SUBSTANCE + 
               APPROPRIATENESS + ORIGINALITY  + CLARITY , data = df2)
summary(model1)



```
## Reviewer confidence disturbution for different ratings of Imapct

```{r echo=TRUE,message=FALSE}
ggplot(data = df, aes(x = REVIEWER_CONFIDENCE)) + geom_bar(fill="purple") +
  facet_wrap(~ IMPACT)+
  labs(
    x = "REVIEWER_CONFIDENCE",
    y = "IMPACT",
    title = "Show each IMPACT rating",
    subtitle = "with each CONFIDENCE rating"
  )
```


## Reviewer confidence disturbution for different ratings of Originality



```{r echo=TRUE,message=FALSE}
ggplot(data = df, aes(x = REVIEWER_CONFIDENCE)) + geom_bar(fill="red4") +
  facet_wrap(~ ORIGINALITY)+
  labs(
    x = "REVIEWER_CONFIDENCE",
    y = "ORIGINALITY",
    title = "Show each ORIGINALITY rating",
    subtitle = "with each CONFIDENCE rating"
  )
```

## Reviewer confidence disturbution for different ratings of Approriateness


```{r echo=TRUE,message=FALSE}
ggplot(data = df, aes(x = REVIEWER_CONFIDENCE)) + geom_bar(fill="orange2") +
  facet_wrap(~ APPROPRIATENESS)+
  labs(
    x = "REVIEWER_CONFIDENCE",
    y = "APPROPRIATENESS",
    title = "Show each APPROPRIATENESS rating",
    subtitle = "with each CONFIDENCE rating"
  )
```
```{r echo=TRUE,message=FALSE}
df4 <- df[, c("REVIEWER_CONFIDENCE", "conference")]
df4 %>% filter(df4$conference == "acl_2017")

```


## Reviewer confidence disturbution for ACL 2017 conference 


```{r echo=TRUE,message=FALSE}
ggplot(df4, aes(x= REVIEWER_CONFIDENCE))+
  geom_bar(fill = "#FF6666")+theme_classic() + labs(
    x = "Reviewer confidence",
    y = "numbr of ratings",
    title = "Reviewer confidence disturbution for ACL 2017 conference",
   
  )

```

## Q2


## Loading csv file



```{r echo=TRUE,message=FALSE}
options(warn = -1)
library(readr)
library(dplyr)
library(stringr)
library(tidytext)
library(ggplot2)
library(stopwords)
options(warn = -1)

reviews <- read_csv("C://Users//Amit//Downloads//Data11.csv")
```



## Getting rid of stop words


```{r echo=TRUE,message=FALSE}
enstopwords<-data.frame(word = c(stopwords("en"),"paper", "authors","model","work","results",
                                 "also","line","section","task","data","table","word","one","can",
                                 "words","1","2","5","6","e.g","3"
                                 ,"models","two","see","al"
                                 ,"system","et","4","use","using","proposed","approach","â","column",
                                 "sections","tasks","allow","based",
                                 "training","dataset",
                                 "language","topics","goal","mean","values","approach","languages",
                                 "think","method","text","set","weaknesses"
                                 ,"used","well","discussion","lines",
                                 "seg","zh","ctc","da","lattice","dmsr","rows","ud","l","weaknesses"))

set.seed(12345)  

reviews4 <- filter(reviews,REVIEWER_CONFIDENCE ==4 )
reviews4<- sample_n(reviews4, 55) 
reviews1 <- filter(reviews,REVIEWER_CONFIDENCE !=4 )

reviews <- union(reviews1,reviews4)
original <- tibble(text = reviews$comments, category = reviews$REVIEWER_CONFIDENCE)

```


## Counting Reviewer confidence


```{r echo=TRUE,message=FALSE}

reviews %>%
  count(REVIEWER_CONFIDENCE) %>%
  ungroup
```


## Plotting Reviewer confidence using negative and positive semantic 

```{r echo=TRUE,message=FALSE}
stack_words <- original %>%
  unnest_tokens(word, text) %>%
  count(category, word, sort = TRUE) %>%
   inner_join(get_sentiments("bing")) %>%
  ungroup()

stack_words <- stack_words %>%bind_tf_idf(word, category, n) 
stack_words <- anti_join(stack_words, enstopwords, by ="word")


original1<-original %>% 
          unnest_tokens(word, text) %>%
          inner_join(get_sentiments("bing")) %>%
          count(word, sentiment,category, sort = TRUE)


original1 <- anti_join(original1, enstopwords, by ="word")


original1 %>%
  filter(n > 12) %>%
  mutate(word = reorder(word, n)) %>%
  mutate(percent = round(n/sum(n), 3)) %>%
  mutate(counts = n) %>%
  ggplot(aes(x = word, y = counts, fill = as.character(category), label = percent)) +
  geom_col(show.legend = TRUE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(title = "Comapre reviews to bing",fill="Reviewer confidence") +
  coord_flip() +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```


## Plotting reviewer confidence according to tf idf

```{r echo=TRUE,message=FALSE}
plot_stack <- stack_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  mutate(category = factor(category, levels = c("1","2",
                                                "3","4",
                                                "5")))

ggplot(plot_stack[1:20,], aes(word, tf_idf, fill = category)) +
  geom_bar(stat = "identity") +
  labs(title = "Arrangment of words according to tf idf",x = NULL, y = "tf-idf" ,fill="Reviewer confidence") +
  coord_flip()
```

## Words disturbution for different reviewer confidence ratings

```{r echo=TRUE,message=FALSE}
plot_stack <- plot_stack %>%
  group_by(category) %>%
  top_n(7, tf_idf) %>%
  mutate(word = reorder(word, tf_idf))

ggplot(plot_stack, aes(word, tf_idf, fill = category)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~category, ncol = 2, scales = "free") +
  ggtitle("TF-IDF on content") +
  coord_flip()

```





